---
title: "Course09 - Week 3 Assignment"
author: "Henrique I. Neves"
date: "19/03/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```

## Course 09 - Week 3 Assignment
A simple slide presentation as the peer review process for the Data Science Specialization.

In this assignment, a simple presentation on R Markdown in presented, that contain a
graph done with plotly package.

## The dataset
To show the different graph, we are going to work with the *mtcars* dataset, which contain several numerical data:
```{r, verbose = FALSE}
head(mtcars)
```

## Graph 1
A histogram with the data from the **carb** column in mtcars:
```{r, echo = FALSE}
plot_ly(x = mtcars$carb, type = "histogram")
```

## Graph 2
Is the displacement related with the gross horse power?
```{r, echo = FALSE, error = FALSE}
plot_ly(data = mtcars, x = ~hp, y = ~disp, type = 'scatter', mode = 'markers')
```
It appears that yes.

## Graph3
A 2D histogram... because why not?
```{r, echo = FALSE}
plot_ly(data = mtcars, x = ~cyl, y = ~gear, type = "histogram2d")
```

## That's all folks!
Thank you for your attention!

Have a nice week.
